\section{The Duration of the Match}\label{sec:duration-of-the-match}

\subsection{Periods of Play}
The match lasts two equal periods of \removed{10} \added{5} minutes, unless otherwise mutually agreed between the referee and the two participating teams.
Any agreement to alter the periods of play (for example, to reduce each half to 3.5 minutes because of a limited schedule) must be made before the start of play and must comply with competition rules.

\subsection{Half-Time Interval}
Teams are entitled to an interval at half time.
The half-time interval must not exceed 5 minutes.
The duration of the half-time interval may be altered only with the consent of both teams and the referee.

\subsection{Timeouts}\label{subsec:duration-of-the-match-timeouts}
Each team is allocated four timeouts at the beginning of the match.
A total of 5 minutes is allowed for all timeouts.
For example, a team may take three timeouts of one-minute duration and thereafter have only one timeout of up to two minutes duration.
Timeouts may only be taken during a game stoppage.
The time is monitored and recorded by the \removed{assistant referee}\added{Referee box operator}.

\subsection{Allowance for Time Lost}
Allowance is made in either period for all time lost through:

\begin{itemize}
\item substitution(s)
\item assessment of damage to robots
\item removal of damaged robots from the field of play for treatment
\item wasting time
\item any other cause
\end{itemize}

The allowance for time lost is at the discretion of the referee.

\subsection{Extra Time}
Competition rules may provide for two further equal periods to be played.
The conditions of \autoref{sec:start-and-restart-of-play} will apply.

\subsection{Abandoned Match}
See \autoref{app:competition-rules}.

\subsection*{Decisions of the Small Size League Technical Committee}
\begin{enumerate}
\item
The local organising committee will make every effort to provide both teams access to the competition area at least two hours before the start of the competition.
They will also strive to allow at least one hour of setup time before each match.
Participants should be aware, however, that conditions may arise where this much time cannot be provided.

\item
Within these rules, the term ``game stoppage'' is used to describe the times when the gameplay is in a stopped state.
Gameplay is not considered stopped when any robot is allowed to kick the ball.
For example, gameplay is stopped after the ``Kickoff'' command has been issued, but it is no longer stopped after the corresponding ``Ready'' command has been issued.
Similarly, gameplay is no longer stopped after a ``Freekick'' has been issued.

\item
\added{The game time does not proceed when the game is in a stopped state.}
\end{enumerate}
